\subsection{Purpose}

The \textbf{AgriHome Vision Console} is a web-based monitoring and decision-support product for controlled-environment agriculture and laboratory plant studies. Operators and researchers use it to observe tray-level imagery, track individual plants, review automated health assessments, organize trays into logical \textbf{meshes}, and manage image-capture schedules. This \textbf{Architectural Design Specification (ADS)} records how the product is decomposed into layers and subsystems, how data moves among them, and which interfaces connect internal components to each other and to external partners.

This document is a companion to the team's \textbf{System Requirements Specification (SRS)} for the same project.\cite{srs} The SRS states \emph{what} the system must do for customers (for example, plant health presentation, automatic capture, environmental data, dashboards, authentication, and secure storage). This ADS states \emph{how} those responsibilities are allocated to software structure: presentation, application orchestration, processing (vision and analytics adapters), and persistent data.

\subsection{Scope}

\textbf{In scope} for this ADS are: the logical four-layer architecture; subsystem names, assumptions, responsibilities, and interface summaries; major data flows from user action to storage; identification of optional processing and search backends; and deployment context at the level of application, database, and object storage.

\textbf{Out of scope} are: user-interface visual design mockups beyond structural responsibilities; detailed REST or GraphQL field specifications; source file paths and build commands (covered in engineering documentation); formal threat models; and training procedures for ML models.

\subsection{System summary}

AgriHome addresses limitations of ad hoc spreadsheets, disconnected camera feeds, and manual record-keeping by providing a \textbf{single console} that ties together:

\begin{itemize}
  \item \textbf{Identity and access} — authenticated users interact only with their permitted trays, plants, and meshes.
  \item \textbf{Observation} — latest captures, charts, and monitoring history support the requirements for plant status display, historical data, and dashboard-style summaries.
  \item \textbf{Interpretation} — health reports and optional model-backed inference enrich raw imagery (where configured).
  \item \textbf{Planning} — schedules express when captures or checks should occur, supporting automatic image capture policies described in the SRS.
  \item \textbf{Persistence} — relational storage holds authoritative domain state; object storage holds images and large artifacts referenced from that state.
\end{itemize}

The reference implementation uses a modern full-stack web platform (browser and installable PWA client, server-hosted application, PostgreSQL, file storage, Firebase Authentication, and optional HTTP-based inference services). The architecture in this document is described so that those technologies could be substituted behind the same layer boundaries where a future maintainer requires it.

\subsection{Document organization}

Section~2 presents the \textbf{project overview} and describes the four primary layers. Section~3 gives a \textbf{system description} with a consolidated subsystem-and-data-flow view. Sections~4--7 document \textbf{data}, \textbf{presentation}, \textbf{application}, and \textbf{processing} layer subsystems respectively, each with assumptions, responsibilities, and interface tables. The \textbf{References} section lists external citations and the companion SRS.
